gtsummary

### 2020-12-11 rmarkdown-gtsummary.Rmd
updates

@@

>>>>

To report the result for `age`, use the following commands inline.

> `` `r
inline_text(tbl_uvregression_1, variable = age)` ``

Here's how the line will appear in your report.

> `r inline_text(tbl_uvregression_1, variable = age)`

@@

```{r, echo=TRUE}
theme_gtsummary_journal("nejm")

tbl_nejm <-
  glm(response ~ age + grade, trial, family = binomial) %>%
  tbl_regression(exponentiate = TRUE)
```

```{r, echo=FALSE, include = FALSE}
tbl_nejm %>% 
  as_gt() %>%
  gtsave(file = "nejm.png")
```
